Music Perception: Stimuli profiles

### 2021-02-25 material/expstimuli/stimuli.Rmd
change loop number
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# stimuli for practice trials
for (i in 97:104){ # 4 stimuli for each category
  subject = list_include$SubNr[i]
  block = list_include$BlockNr[i]
  trial = list_include$TrialNr[i]
  cond = list_include$Condition[i]
  skill = list_include$Skill[i]
  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
  firstTimestamp = current$TimeStamp[1]
  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0

>>>>

# stimuli for practice trials
for (i in 73:80){ # 4 stimuli for each category
  subject = list_include$SubNr[i]
  block = list_include$BlockNr[i]
  trial = list_include$TrialNr[i]
  cond = list_include$Condition[i]
  skill = list_include$Skill[i]
  current <- dt_include[SubNr == subject & BlockNr == block & TrialNr == trial]
  firstTimestamp = current$TimeStamp[1]
  current$TimeStamp <- current$TimeStamp - firstTimestamp # start with time 0
